The Cluster Difference Imaging Photometric Survey (CDIPS). I. Method \& TESS Light Curves from Sector 6

### 2019-05-20 paper/ms.tex
paper: star selection before phot methods
paper: add magfit discn

\shortauthors{Bouma et al.}
\shorttitle{Light Curves for Stars in Clusters}

@@

Cluster stars have been monitored photometrically from the ground
(CITE: Joel thesis, Cambridge group).
A few clusters, NAME1 and NAME2, were observed by Kepler in its prime
mission (CITE: Meibom).
And a few more, most notably including X,Y,Z, were observed in K2's
ecliptic mission (CITE).

@@

We reduced the TESS images to lightcurves by performing a sequence of
steps using stand-alone programs.  A conceptual overview of our
``pipeline'' is given in Figure~\ref{fig:pipeline}.  
Our overall method is in the spirit of the reduction approaches used
by \citet{Pal_2009}, \citet{soares-furtado_image_2017} and
\citet{oelkers_precision_2018}.

We begin with the calibrated full frame images produced by SPOC
(\S~\ref{subsec:observations}).  We then perform a collection of
preparatory steps, including source extraction of bright stars,
astrometry using the resulting positions, and coarse simple aperture
photometry (\S~\ref{subsec:preparation}).  Using the shape values from
the initial astrometry, we select an astrometric reference frame and
transform all of the calibrated images to it.  We construct a
photometric reference by stacking a collection of frames, and then
convolve all the transformed frames to the photometric reference,
and subtract (\S~\ref{subsec:imagesubtraction}).  We perform aperture
photometry on the subtracted images using positions projected onto the
frame from Gaia DR2.  We detrend the resulting lightcurves
(\S~\ref{subsec:lcdetrending}).
We then select stars that we believe are ``cluster members'',
roughly X\% of the overall dataset (\S~\ref{sec:starselection}).
Focusing on the lightcurves of these stars, their white noise and red
noise properties, and point out a few interesting cases of
variability (\S~\ref{sec:results}).

@@

The preceding steps produce lightcurves that include both instrumental
systematics as well as astrophysical variability.  The detrending
philosophy adopted by the HAT group typically proceeeds in two
sequential stages (see discussions from {\it e.g.}
\citealt{bakos_2010,huang_high-precision_2015,zhang_precision_2016}) .
The first stage is to decorrelate against external parameters that are
known to affect the stellar flux measurements (EPD,
\citealt{bakos_2010}). The second stage is to filter remaining
systematic trends caused by unknown parameters by decorrelating the
measured brightnesses of stars against each other (TFA,
\citealt{kovacs_trend_2005}).

%FIXME TURGID PROSE
In general though, one must adapt detrending procedures to the data at
hand.  In \S~\ref{sec:flux_vs_external_parameters}, we show that the
``external parameter'' dependence visible in the TESS data is rather
complex: ordinary linear model-fitting, as well as an initial attempts
at non-linear model fitting, are poor descriptions of the data.  We go
on to show (\S~\ref{sec:tfa_is_good_enough}) that a plausible
detrending approach for the purpose of transit discovery is to simply
decorrelate against other nearby stars with standard TFA.

>>>>

\shortauthors{Bouma et al.}
\shorttitle{CDIPS I: Method \& Sector 6}

@@

Cluster stars have been monitored photometrically from the ground
(CITE: Joel thesis, Cambridge group).
A few clusters, NAME1 and NAME2, were observed by Kepler in its prime
mission (CITE: Meibom).
And a few more, most notably X,Y, and Z, were observed in K2's
ecliptic mission (CITE).

@@

We reduced the TESS images to lightcurves by performing a sequence of
steps using stand-alone programs.  A conceptual overview of our
pipeline is given in Figure~\ref{fig:pipeline}.  
Our overall method is in the spirit of the reduction approaches used
by \citet{Pal_2009}, \citet{soares-furtado_image_2017} and
\citet{oelkers_precision_2018}.

We begin with the calibrated full frame images produced by SPOC
(\S~\ref{subsec:observations}).  We then perform a collection of
preparatory steps, including source extraction of bright stars,
astrometric calibration, and coarse simple aperture
photometry (\S~\ref{subsec:preparation}).  Using the shape values from
the initial astrometry, we select an astrometric reference frame to
which we transform all of the calibrated images.  We construct a
photometric reference by stacking a collection of frames, and then
convolve all the transformed frames to the photometric reference, and
subtract (\S~\ref{subsec:imagesubtraction}).  We perform aperture
photometry on the subtracted images using positions projected onto the
frame from Gaia DR2.  We detrend the resulting lightcurves
(\S~\ref{subsec:lcdetrending}).  We then select stars that we believe
are ``cluster members'', roughly X\% of the overall dataset
(\S~\ref{sec:starselection}).  Focusing on the lightcurves of these
stars, their white noise and red noise properties, and point out a few
interesting cases of variability (\S~\ref{sec:results}).

@@

The preceding steps produce lightcurves that include both instrumental
systematics as well as astrophysical variability.  The detrending
approach adopted by the HAT group typically proceeeds in a few
sequential stages (see discussions from {\it e.g.}
\citealt{bakos_2010,huang_high-precision_2015,zhang_precision_2016}).
Given the heritage of our pipeline, we briefly discuss these, and then
explain why we omit most of the steps described.

The first detrending step commonly performed on ground-based data is
``magnitude-fitting'': the raw magnitudes measured from the difference
images are fit by a polynomial that depends on a combination of CCD
position, sub-pixel position, and optionally catalog magnitude and
color.

The second step is to decorrelate against external parameters that are
known to affect the stellar flux measurements (EPD,
\citealt{bakos_2010}).  For ground-based data this may include zenith
angle, or changing PSF parameters.  For TESS data, this might include
CCD temperature, or perhaps a measure of the scatter in the spacecraft
pointing (CITE: Vanderburg 2019).

The final step is to then decorrelate the measured brightnesses of
stars against each other (TFA, \citealt{kovacs_trend_2005}).  
This accounts for variations due to unknown systematic effects that
affect many stars.

%FIXME TURGID PROSE
In general though, one must adapt detrending procedures to the data at
hand.  In \S~\ref{sec:flux_vs_external_parameters}, we show that the
``external parameter'' dependence visible in the TESS data is rather
complex: ordinary linear model-fitting, as well as an initial attempts
at non-linear model fitting, are poor descriptions of the data.  
In a similar vein ``magnitude-fitting'' is minimally justified, given
how the TESS magnitudes correlate against these external parameters.
We go on to show (\S~\ref{sec:tfa_is_good_enough}) that a plausible
detrending approach for the purpose of transit discovery is to simply
decorrelate against other nearby stars with standard TFA.
